Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2021-03-20 main.tex
:pencil: Update algorithms

			\begin{figure*}[!b]
				\hrule
				\begin{equation}
					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:z_expand}
				\end{equation}
				\begin{flalign}
					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},&&\label{eq:y_I2}\\
					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,&&\label{eq:y_I4}
				\end{flalign}
				\begin{flalign}
					\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},&&\label{eq:y_P2}\\
					\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.&&\label{eq:y_P4}
				\end{flalign}
			\end{figure*}
			% \begin{figure*}[!b]
			% 	\hrule
			% 	\begin{align}
			% 		z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) & = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)\nonumber\\
			% 		& \quad + \beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
			% 	\end{align}
			% 	\hrule
			% 	\begin{align}
			% 		\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
			% 		& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
			% 		\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
			% 		& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
			% 		\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
			% 		& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
			% 		\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
			% 		& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*}\nonumber\\
			% 		& = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
			% 	\end{align}
			% \end{figure*}
		\end{subsection}

		\begin{subsection}{Rate-Energy Region}
			The achievable R-E region is defined as
			\begin{align}
				C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P)
				&\triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z,\nonumber\\
				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
			\end{align}
			% \begin{equation}
			% 	C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P) \triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z, \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
			% \end{equation}
			where $P$ is the average transmit power budget and \num{1/2} converts the peak value to the average value.
		\end{subsection}
	\end{section}

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize each R-E boundary point through a current maximization problem subject to transmit power, IRS magnitude, and rate constraint
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1.}
		\end{maxi!}
		Problem~\eqref{op:original} is intricate with coupled variables in non-convex expressions \eqref{ob:original}, \eqref{co:original_rate}, \eqref{co:original_modulus}. To obtain a feasible solution, we propose an BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and the splitting ratio, until convergence.
		% \begin{remark}\label{re:irs_subchannel_alignment}
		% 	As information and power transfer prefer different subchannel strength distribution, the frequency-flat characteristic of the IRS introduces a resource allocation problem. Following Remark~\ref{re:irs_frequency_flat}, if the IRS is frequency-selective and there is only one transmit antenna, then each reflecting element can simultaneously align the corresponding AP-IRS-UE channel with the AP-UE channel at all subbands. In this case, the strengths of all subchannels are maximized so that the joint design would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
		% \end{remark}

		\begin{subsection}{Passive Beamforming}
			In this section, we optimize the IRS phase shift $\boldsymbol{\phi}$ for any given waveform $\boldsymbol{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. Note that
			\begin{align}
				\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2
				& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
				& = \boldsymbol{w}_{\mathrm{I},n}^H(\boldsymbol{h}_{\mathrm{D},n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{\mathrm{D},n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
				& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
			\end{align}
			where $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\mathrm{D},n}]^H \in \mathbb{C}^{(L+1) \times M}$, $t$ is an auxiliary variable with unit modulus, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$. On the other hand, we define $t_{\mathrm{I/P},k}$ as
			\begin{align}
				t_{\mathrm{I/P},k}
				& \triangleq \boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{h}\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
				& = \mathrm{Tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{\mathrm{I/P},k}\right)\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})
			\end{align}
			where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\mathrm{I/P},k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, we can rewrite \ref{eq:R} and \ref{eq:z_expand} as
			\begin{align}
				R(\boldsymbol{\Phi})
				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
				z(\boldsymbol{\Phi})
				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})\nonumber\\
				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
			\end{align}
			% \begin{align}
			% 	R(\boldsymbol{\Phi})
			% 	& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
			% 	z(\boldsymbol{\Phi})
			% 	& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right) + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
			% \end{align}
			To maximize the non-concave expression \eqref{eq:z_irs}, we propose a SCA algorithm and lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}. Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
			\begin{align}
				(t_{\mathrm{I},0}^{(i)})^2
				& \ge 2 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - (t_{\mathrm{I},0}^{(i-1)})^2,\label{eq:taylor_1}\\
				t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i)})^*

>>>>

			\begin{figure*}[!b]
				\hrule
				\begin{flalign}
					z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),&&\label{eq:z_expand}
				\end{flalign}
				\begin{flalign}
					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},&&\label{eq:y_I2}\\
					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,&&\label{eq:y_I4}
				\end{flalign}
				\begin{flalign}
					\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},&&\label{eq:y_P2}\\
					\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.&&\label{eq:y_P4}
				\end{flalign}
			\end{figure*}
		\end{subsection}

		\begin{subsection}{Rate-Energy Region}
			The achievable R-E region is defined as
			\begin{align}
				C_{R_{\mathrm{ID}}-I_{\mathrm{EH}}}(P)
				&\triangleq \biggl\{(R_{\mathrm{ID}}, I_{\mathrm{EH}}): R_{\mathrm{ID}} \le R, I_{\mathrm{EH}} \le z,\nonumber\\
				&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\}
			\end{align}
			where $P$ is the average transmit power budget and \num{1/2} converts the peak value to the average value.
		\end{subsection}
	\end{section}

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize each R-E boundary point through a current maximization problem subject to transmit power, IRS magnitude, and rate constraint as
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1.}
		\end{maxi!}

		Problem~\eqref{op:original} is intricate with coupled variables in non-convex expressions \eqref{ob:original}, \eqref{co:original_rate}, \eqref{co:original_modulus}. To obtain a feasible solution, we propose an BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and the splitting ratio, until convergence.
		% \begin{remark}\label{re:irs_subchannel_alignment}
		% 	As information and power transfer prefer different subchannel strength distribution, the frequency-flat characteristic of the IRS introduces a resource allocation problem. Following Remark~\ref{re:irs_frequency_flat}, if the IRS is frequency-selective and there is only one transmit antenna, then each reflecting element can simultaneously align the corresponding AP-IRS-UE channel with the AP-UE channel at all subbands. In this case, the strengths of all subchannels are maximized so that the joint design would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
		% \end{remark}

		\begin{subsection}{Passive Beamforming}
			In this section, we optimize the IRS phase shift $\boldsymbol{\phi}$ for any given waveform $\boldsymbol{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. Note that
			\begin{align}
				\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2
				& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
				& = \boldsymbol{w}_{\mathrm{I},n}^H(\boldsymbol{h}_{\mathrm{D},n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{\mathrm{D},n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
				& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})
			\end{align}
			where $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\mathrm{D},n}]^H \in \mathbb{C}^{(L+1) \times M}$, $t'$ is an auxiliary variable with unit modulus, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t']^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$. On the other hand, we define $t_{\mathrm{I/P},k}$ as
			\begin{align}
				t_{\mathrm{I/P},k}
				& \triangleq \boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{h}\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
				& = \mathrm{Tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{\mathrm{I/P},k}\right)\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
				& = \mathrm{Tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})
			\end{align}
			where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\mathrm{I/P},k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. On top of this, \eqref{eq:R} and \eqref{eq:z_expand} reduce to
			\begin{align}
				R(\boldsymbol{\Phi})
				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
				z(\boldsymbol{\Phi})
				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})\nonumber\\
				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
			\end{align}

			To maximize the non-concave expression \eqref{eq:z_irs}, we propose a SCA algorithm and lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}. Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
			\begin{align}
				(t_{\mathrm{I},0}^{(i)})^2
				& \ge 2 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - (t_{\mathrm{I},0}^{(i-1)})^2,\label{eq:taylor_1}\\
				t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i)})^*
				& \ge 2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*,\label{eq:taylor_2}\\
				t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)}
				& = \frac{1}{4}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\nonumber\\
				& \ge \frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})\nonumber\\
				& \quad - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\label{eq:taylor_3}
			\end{align}

			Plugging \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} into \eqref{eq:z_irs}, we obtain the DC current approximation \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
			\begin{figure*}[!b]
				\hrule
				\begin{align}
					\tilde{z}(\boldsymbol{\Phi}^{(i)})
					& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)})\nonumber\\
					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\right).\label{eq:z_irs_approx}
				\end{align}
			\end{figure*}
			\begin{maxi!}
				{\boldsymbol{\Phi}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
				\addConstraint{\boldsymbol{\Phi}_{l',l'}=1, \quad l'=1,\dots,L+1}\label{co:irs_modulus}
				\addConstraint{\boldsymbol{\Phi}\succeq{0}}\label{co:irs_sd}
				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_rank}}
			\end{maxi!}
